Robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives

### 2017-06-16 paper/paper.tex
[minor] comments from sensei
[major] add updated presentation for conference

where desired acceleration $\dot{v}(t)$ can be calculated by double differentiating position data recorded from demonstration as

@@

\section{Experiments}
\label{sec:experiments}
Robotic cloth manipulation task contains a dual arm humanoid robot Baxter. Setup of our system is shown in figure \ref{fig:setup}. We choose soft mannequin instead of a human for this experiment. Both the arms of mannequin are open and given support by a metallic stand, to avoid falling down. Mannequin is positioned in such a way so that it resides within limits of workspace of Baxter robot. Both the arms of mannequin are facing towards robot. A Kinect V2 \cite{microsoft2014kinect} sensor is mounted on LCD display of Baxter robot. Kinect sensor can see the mannequin and clothing article and provides depth information, which is necessary for mannequin tracking. The clothing article is put in the arms of Baxter robot manually before starting experiment.

Baxter robot is connected to a computer directly using Ethernet cable. It is controlled using Robot Operating System (ROS) \cite{quigley2009ros}, one of the widely used tools by the researchers in robotics community. We used Baxter robot's API, which is available and supported by ROS to command the robot. Kinect sensor is controlled by open source Kinect API for ROS \cite{iai_kinect2, libfreenect2}. We performed following two experiments to validate our approach: (a) Clothing task using position DMP (b) Failure detection using end-effector forces.

\subsection{Clothing task using position DMP}
The aim of this experiment is to put sleeveless T-shirt on both the arms of mannequin by using DMP system. We use position data to initialize DMP system, which is being used in this task. The posture of mannequin is changed. At this point, we use Kinect Sensor to get 3D coordinates of wrist and shoulder of mannequin. Now we change start and goal parameter of initial DMP system by using this information. Modified DMP can be acquired by rolling out initial DMP system as described in section \ref{sec:dmp}.

>>>>

where desired acceleration $\dot{v}(t)$ can be calculated by taking second derivative of the positional data recorded from demonstration as

@@

\section{Experiments}
\label{sec:experiments}
\subsection{Clothing task using position DMP}
The aim of this experiment is to put sleeveless T-shirt on both the arms of mannequin by using DMP system. We use position data to initialize DMP system, which is being used in this task. The posture of mannequin is changed. At this point, we use Kinect Sensor to get 3D coordinates of wrist and shoulder of mannequin. Now we change start and goal parameter of initial DMP system by using this information. Modified DMP can be acquired by rolling out initial DMP system as described in section \ref{sec:dmp}.

### 2017-06-16 presentation/presentation.tex
[major] add updated presentation for conference

%\setbeamerfont{author}{size=\footcitesize}
%\setbeamerfont{institute}{size=\tiny}
\setbeamertemplate{navigation symbols}{}
\renewcommand{\footnotesize}{\tiny}

\title[AIR 2017]{Robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives}
\author[Ravi P. Joshi]{Ravi P. Joshi$^a$, Nishanth Koganti$^{a,b}$, and Tomohiro Shibata$^a$}
\institute[]{\tiny{$^a$ Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Kitakyushu, Japan\\$^b$ Graduate School of Information Science, Nara Institute of Science and Technology, Nara, Japan}}

\date[]{{June 28, 2017}}
%\date[]{}

@@

\begin{document}
{
  \usebackgroundtemplate{\includegraphics[width=\paperwidth]{background.pdf}}
  \setbeamertemplate{footline}{} 
  \begin{frame}
    \titlepage
  \end{frame}
}
\addtocounter{framenumber}{-1}

@@

\section{Introduction}
\begin{frame}{Introduction}
	\linespread{1.6}

	\begin{itemize}
		\item Clothing assistance is a basic and important assistance activity in the daily life of the elderly and disabled people
		\item Need of robotic clothing assistance is growing
	\end{itemize}

@@

	\vskip -1em
	\begin{columns}[t]
		\begin{column}{0.5\textwidth}
			Towner \textit{et al.}\footnotemark, ~Identifying and manipulating clothing article by dual-arm robot
			{\scriptsize
				\begin{itemize}
					\item[\color{green}{\checkmark}] Used Hidden Markov Model for tracking
					\item[\color{green}{\checkmark}] Triangulated mesh model for simulating clothing article
					\item[\color{red}{$\times$}] Simple manipulations such as gripping using one arm only
				\end{itemize}
			}
			\vskip 0.5em
			\centering{
				\includegraphics[height=2.5cm]{towner_2011}
			}
		\end{column}

@@

\section{Setup and Experiment}
\begin{frame}{Workflow of \textit{Robotic cloth manipulation} task}
	\vskip -0.5em
	\begin{figure}
		\includegraphics[width=0.85\textwidth]{flowchart_beamer_hd}
	\end{figure}
\end{frame}

@@

	\begin{itemize}
		\item Result shows that DMPs are able to generalize the movement trajectory
		\item The converted trajectory from Cartesian Space to Joint Space was not smooth in some regions
		      \begin{itemize}
		      	\item It was calculated using \textsc{Trac\_IK}\footcite{beeson2015trac}
		      \end{itemize}
		\item Also real-time tracking of mannequin is required
	\end{itemize}
\end{frame}

\section{Future work}
\begin{frame}{Tentative Research Plan}

	\begin{figure}
		\includegraphics[width=\textwidth]{timeline}
	\end{figure}
\end{frame}

>>>>

\setbeamertemplate{navigation symbols}{}
\renewcommand{\footnotesize}{\tiny}

\title[AIR 2017]{Robotic cloth manipulation for clothing assistance task using Dynamic Movement Primitives}
\author[Ravi P. Joshi]{Ravi P. Joshi$^a$, Nishanth Koganti$^{a,b}$, and Tomohiro Shibata$^a$}
\institute[]{\tiny{$^a$Graduate School of Life Science and Systems Engineering, Kyushu Institute of Technology, Kitakyushu, Japan\\$^b$Graduate School of Information Science, Nara Institute of Science and Technology, Nara, Japan}}

\date[]{{June 29, 2017}}

@@

\begin{document}
{
	\usebackgroundtemplate{\includegraphics[width=\paperwidth]{background}}
	\setbeamertemplate{footline}{} 
	\begin{frame}
		\titlepage
	\end{frame}
}
\addtocounter{framenumber}{-1}

@@

\section{Introduction}
\begin{frame}{Introduction}
	\linespread{1.5}
	\begin{columns}[t]
		\begin{column}{0.65\textwidth}
			\begin{itemize}
				\item Clothing assistance is a basic and important assistance activity in the daily life of the elderly and disabled people
				\item Need of robotic clothing assistance is growing
			\end{itemize}
		\end{column}

		\begin{column}{0.35\textwidth}
			\begin{figure}
				\includegraphics[width=0.8\textwidth]{robotic_clothing_assistance}
			\end{figure}
		\end{column}
	\end{columns}

@@

	\vskip -1em
	\begin{columns}[t]
		\begin{column}{0.5\textwidth}
			Towner \textit{et al.}\footnotemark, ~Identifying and manipulating clothing article by dual-arm robot
			{\scriptsize
				\begin{itemize}
					\item[\color{green}{\checkmark}] Used Hidden Markov Model for tracking
					\item[\color{green}{\checkmark}] Triangulated mesh model for simulating clothing article
					\item[\color{red}{$\times$}] Highly depends on simulated contour information.
				\end{itemize}
			}
			\vskip 0.5em
			\centering{
				\includegraphics[height=2.5cm]{towner_2011}
			}
		\end{column}

@@

\section{Setup and Experiment}
\begin{frame}{Workflow of \textit{Robotic cloth manipulation} task}
	\vskip -0.5em
	\begin{figure}
		\includegraphics[width=0.9\textwidth]{flowchart_beamer}
	\end{figure}
\end{frame}

@@

	\begin{itemize}
		\item Baxter APIs\footcite{fitzgerald2013developing} are used to get the end-effector forces. Raw forces are found noisy in nature.
		\item Result shows that DMPs are able to generalize the movement trajectory
		\item Proposed failure detection method by using force information can detect failures
		\item DMP should incorporate orientation information as well
	\end{itemize}
\end{frame}

\section{Future work}
\begin{frame}{Future work}
	\linespread{1.5}

	\begin{itemize}
		\item Make approach more robust by using combination of visual and force information
		\item Need for designing an adaptive controller
		      \begin{itemize}
		      	\item For real-time tracking of mannequin
		      	\item To adapt various failure scenarios
		      \end{itemize}
	\end{itemize}

	\begin{exampleblock}{Acknowledgments}
		This work was supported in part by the Grant-in-Aid for Scientific Research from Japan Society for the Promotion of Science (No. 16H01749).
	\end{exampleblock}
\end{frame}
